Water resource utilization regimes at a basin scale: transition framework and development traps

### 2020-10-15 tex/sup/supplementary_information.tex
add a sensitivity analysis section

@@

\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/map.pdf}
	\caption{
		\textbf{The Human Development Index of the world's great river basins, and the major problems facing some basins.}
		Overdependence on water resources for economic development in some basins, and high levels of human modification in others that have disrupted ecosystem structure. Data resources: Human Development Index in each basin refers from \cite{linkeGlobalHydroenvironmentalSubbasin2019}, strongly intervened basins and resource-dependent basins are come from Transboundary River Basins report by United Nations Environment Programme \url{http://geftwap.org/publications/river-basins-technical-report} \cite{unep-dhiTransboundaryRiverBasins2016}.
	}
	\label{fig:traps}
\end{figure}

>>>>

\section*{Sensitive analysis}
% 一个对断点检测方法普遍的批评是可以通过调整方法的使用来操纵结果，因此我们对断点识别的过程进行了敏感性分析，以证明我们的结果是鲁棒性的。
A common criticism of breakpoint detection methods is that the results can be manipulated by adjusting the use of the methods, so we conducted a sensitivity analysis of the breakpoint recognition process to demonstrate that our results are robust.

Firstly, we performed three different normalization methods in construction of IWRU for breakpoint detection:

\begin{itemize}
    \item Min-max normalization:
        $$ normalized(X) = (X - X_{min}) / (X_{max} - X_{min}) $$
    \item Mean-max normalization:
        $$ normalized(X) = (X - X_{mean}) / (X_{max} - X_{min}) $$
    \item Z-score normalization:
        $$ normalized(X) = \frac{X-X_{mean}}{X_{std}} $$ 
\end{itemize}

Where $X$ is a time series and $X_{mean}$, $X_{std}$, $X_{min}$, $X_{max}$ are mean, standard deviation, minimum, maximum of it.
% 无论我们使用上述哪种标准化方法，将三个维度的指标合成为IWRU，我们对IWRU的断点检测结果都相同。
No matter which of the above standardized methods we use in combining the indicators of the three dimensions, and our detection results for IWRU breakpoints are the same.

Another place where there is room for manipulation is the choice of significance threshold (i.e. threshold of the p-value) in the Pettitt Change points detection method. Here, we test 1000 possible p-values between $10^{-6}$ and $0.01$, and most of the results give the same detection in breakpoints. 
It has not given another breakpoint before the threshold is near to $10^{-2}$ (see \textit{SI Appendix} Fig. S12: A). 
% 不仅如此，当三个断点被检测出时，之前的两个断点仍然存在，且新增加的断点带来阶段划分的趋势差异并不明显
Not only that, when three breakpoints are detected, the previous two breakpoints still exist (1978 and 1994), and the trend difference of the new breakpoints is not obvious (see \textit{SI Appendix} Fig. S12: B and C).

Taken together, the results of three periods in this study with the two breakpoints detected (1978 and 1994) are robust.

@@

% 补充图片 11 全球案例
\begin{figure}%[htbp]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/map.pdf}
	\caption{
		\textbf{The Human Development Index of the world's great river basins, and the major problems facing some basins.}
		Overdependence on water resources for economic development in some basins, and high levels of human modification in others that have disrupted ecosystem structure. Data resources: Human Development Index in each basin refers from \cite{linkeGlobalHydroenvironmentalSubbasin2019}, strongly intervened basins and resource-dependent basins are come from Transboundary River Basins report by United Nations Environment Programme \url{http://geftwap.org/publications/river-basins-technical-report} \cite{unep-dhiTransboundaryRiverBasins2016}.
	}
	\label{fig:traps}
\end{figure}

补充图片10：地下水
\begin{figure}
    \centering
    \includegraphics[width=0.95\textwidth]{../../figures/sup/sensitivity.pdf}
    \caption{
        Sensitivity analysis of the threshold of p-values. 
        \textbf{A.} number of breakpoints in different p-values.
        \textbf{B.} A typical result of two breakpoints.
        \textbf{C.} A typical result of three breakpoints.
    }
\end{figure}
